Concurrent Programming in Harmony

### 2021-04-18 book/paper.tex
Latest

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/queuebug1.pdf}
\end{center}
\caption{Harmony output of running \autoref{fig:qtest3} against
\autoref{fig:queuebug}.}
\label{fig:queuebug1}
\end{figure}

@@

Let us run the code through some of the test programs in the last
chapter.  Harmony does not detect any issues with the sequential test
in \autoref{fig:qtestseq}.  The concurrent \texttt{put} test of
\autoref{fig:qtest1} as well as the concurrent \texttt{get} test of
\autoref{fig:qtest2} also find no problems.  However, when we run
the new queue code through the test in \autoref{fig:qtest3}, Harmony
finds a problem.

@@

To fix the code, we have to use hand-over-hand locking (\autoref{ch:cds}).
\autoref{fig:queuefix} shows an implementation that uses the same
data structure as \autoref{fig:queuebug} but uses hand-over-hand locking,
both for \texttt{put}() and for \texttt{get}().  It passes all tests.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/queuebug1.pdf}
\end{center}
\caption{\harmonyref{queuebug.html}{Harmony output of running \autoref{fig:qtest3} against
\autoref{fig:queuebug}}.}
\label{fig:queuebug1}
\end{figure}

@@

Let us run the code through some of the test programs in the last
chapter.  Harmony does not detect any issues with the sequential test
in \autoref{fig:qtestseq}.
(Run this using the \texttt{-m} flag like this:
\texttt{harmony -m queue=queuebug code/qtestseq.hny})
The concurrent \texttt{put} test of
\autoref{fig:qtest1} as well as the concurrent \texttt{get} test of
\autoref{fig:qtest2} also find no problems.  However, when we run
the new queue code through the test in \autoref{fig:qtest3}, Harmony
finds a problem.

@@

To fix the code without changing the data structure, we can use
hand-over-hand locking (\autoref{ch:cds}).
\autoref{fig:queuefix} shows an implementation that uses the same
data structure as \autoref{fig:queuebug} but uses hand-over-hand locking,
both for \texttt{put}() and for \texttt{get}().  It passes all tests.
